---
title: "Safe Master File Distribution Workflow"
subtitle: "Source Selection First, Then Audit, Then Distribution"
author: "Dan Swart"
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: false
    code-copy: true
execute:
  echo: true
  warning: false
  message: false
---

## Purpose

This guide is for the **distribution workflow only**.

It is intentionally separate from the large-file audit workflow.

The main idea is:

1. find most recent candidates

2. promote selected files to master

3. audit

4. dry run

5. distribute

6. verify all identical


This makes the workflow safer because it does **not** assume the current master copy is always the best copy.

## Which helper file this guide uses

This guide uses a **new updated helper file**:

`safe_master_file_distribution_helpers_v2.R`

This is a replacement for the earlier helper because the new version adds a full **Step 1 source-selection stage**.

So this guide and the new helper belong together.

## This workflow is separate from the large-file audit workflow

This workflow is **not** the same as the large-file audit workflow.

The large-file audit workflow helps answer questions like:

- Which `.csv`, `.xlsx`, and `.pdf` files are large?
- Which files may cause GitHub problems?
- Which repos have tracked large files?

The distribution workflow answers a different question:

- Which shared standard file should become the official source copy?
- And how do I safely distribute that standard file afterward?

Keep those two workflows separate.

## Recommended folder arrangement

A simple setup is:

- `~/R Working Directory/Master File Distribution Code`
    - stores your official standard files
    - stores `safe_master_file_distribution_helpers_v2.R`
    - stores this `.qmd` guide
- `~/R Working Directory/<project folders>`
    - contain evolving project-specific copies

## Step 0: Source the helper file

Use an explicit path.

```{r}
master_code_dir <- path.expand("~/R Working Directory/Master File Distribution Code")

source(file.path(
  master_code_dir,
  "safe_master_file_distribution_helpers_v2.R"
))
```

## Step 1: Inspect the default file set

```{r}
default_distribution_files("analysis")
```

Other built-in profiles:

```{r}
default_distribution_files("quarto_site")
default_distribution_files("minimal")
```

## Step 2: Find the most recent candidate copy of each shared file

```{r}
scan <- find_most_recent_shared_files()
```

The object contains:

- `scan$most_recent`
- `scan$all_matches`

The `most_recent` table shows the newest candidate file for each shared filename.

```{r}
scan$most_recent
```

The `all_matches` table shows every match that was found.

```{r}
scan$all_matches |> head(100)
```

## Why this step matters

Without this step, the workflow assumes the file currently sitting in `Master File Distribution Code` is the correct source copy.

That assumption can be wrong.

If you have been modifying shared files inside individual project folders, the newest and best copy may live in one of those project folders rather than in the master folder.

So the `find_most_recent_shared_files()` step gives you a better candidate source list before any audit or distribution happens.



## Step 3: Save the most-recent scan to Excel

```{r}
most_recent_file <- write_most_recent_shared_files_excel(
  scan,
  output_dir = "."
)

most_recent_file
```

The workbook includes:

- `most_recent`
- `all_matches`

## Important caution about "most recent"

The most recent file is the best **candidate** source copy.

It is **not automatic proof** that the file should become the official source.

Sometimes the newest file may be:

- a local experiment
- a partial edit
- a project-specific deviation
- a file changed only cosmetically

So you should review the `most_recent` sheet before promoting files into the master folder.


## Step 4: Promote selected files into the master folder

A dry run first:

```{r}
promotion_plan <- promote_files_to_master(
  selected_paths = scan$most_recent$path,
  dry_run = TRUE
)

promotion_plan
```



When satisfied, run the actual promotion:

```{r eval=FALSE}
promotion_result <- promote_files_to_master(
  selected_paths = scan$most_recent$path,
  dry_run = FALSE
)
```


## Step 5: Audit the distribution conflicts

```{r}
audit <- audit_distribution_conflicts()
audit |> head(20)
```



## Step 6: Summarize the audit

```{r}
summary <- summarize_distribution_audit(audit)
summary
```



## Step 7: Save the distribution audit to Excel

```{r}
audit_file <- write_distribution_audit_excel(
  audit,
  summary = summary,
  output_dir = "."
)

audit_file
```



## How to interpret the distribution statuses

The main status column is `compare_status`.

- `different_source_newer`: master source appears newer  

- `identical`: source and destination match  

- `missing_destination`: the destination file does not exist  

- `missing_source`: the source file is missing from the master folder

- `different_destination_newer`: destination appears newer  

- `different_same_or_unknown_time`: files differ but timestamps do not clearly settle it  


The most important warning state is:

`different_destination_newer`

It may mean the project has a newer local version that you do not want to overwrite automatically.




## Step 8: Focus on the risky rows first

```{r}
audit |>
  dplyr::filter(compare_status %in% c(
    "different_destination_newer",
    "different_same_or_unknown_time"
  ))
```

Get status conditions report

```{r}
audit |>
  dplyr::count(compare_status, recommended_action, sort = TRUE)
```



## Step 9: Dry run the distribution plan

```{r}
plan <- distribute_project_files_safe(dry_run = TRUE)
```


```{r}
plan |>
  dplyr::count(compare_status, will_copy, sort = TRUE)
```


Inspect the planned actions:

```{r}
plan |>
  dplyr::select(
    repo_name,
    file_name,
    compare_status,
    recommended_action,
    will_copy
  ) |>
  head(50)
```



## Step 10: Run the actual distribution

Only after reviewing the audit and dry run:

```{r eval=FALSE}
result <- distribute_project_files_safe(dry_run = FALSE)
```

## Step 11: Verification

The final verification step is a fresh distribution audit.  If the workflow completed successfully, the compare-status table should show only identical.


### First verification

```{r}
audit_after <- audit_distribution_conflicts()

all_identical <- audit_after |>
  dplyr::summarise(all_identical = all(compare_status == "identical")) |>
  dplyr::pull(all_identical)

all_identical
```


### Second verification

```{r}
audit_after <- audit_distribution_conflicts()

status_check <- audit_after |>
  dplyr::count(compare_status, sort = TRUE)

status_check

all(status_check$compare_status == "identical")
```





Default protections are conservative:

- `overwrite_mode = "if_source_newer"`
- `protect_newer_destination = TRUE`
- `backup_before_overwrite = TRUE`


## Most important principle

Do **not** think of this as:

> push the master files everywhere

Think of it as:

> identify the best candidate source file, promote it into the master folder, audit the differences, then copy only when safe

That is the whole reason this workflow is safer than a blind overwrite workflow.



## Final recommendation

This new workflow should replace the earlier distribution workflow.

It adds the missing first step that you correctly identified:

**find the most recent candidate source file first**

Only after that should the master folder become the source of truth for distribution.
