---
title: "Safe Master File Distribution Workflow"
subtitle: "Source Selection First, Then Audit, Then Distribution"
author: "Dan Swart"
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: false
    code-copy: true
execute:
  echo: true
  warning: false
  message: false
---

## Purpose

This guide is for the **distribution workflow only**.

It is intentionally separate from the large-file audit workflow.

The main idea is:

1. first find the **most recent candidate source copy** of each shared file  
2. then promote the chosen files into `Master File Distribution Code`  
3. then audit the distribution results  
4. then dry run the copy plan  
5. then distribute only when satisfied  
6. then verify that everything is identical

This makes the workflow safer because it does **not** assume the current master copy is always the best copy.


## Which helper file this guide uses

This guide uses:

`SAFE_master_file_distribution_helpers_v3.R`

This version includes:
- most-recent source scanning
- safe promotion to the master folder
- optional `Current as of` date-stamp updating during promotion
- audit / dry-run / distribution verification


## This workflow is separate from the large-file audit workflow

This workflow is **not** the same as the large-file audit workflow.

The large-file audit workflow helps answer questions like:

- Which `.csv`, `.xlsx`, and `.pdf` files are so large they cause GitHub problems?
- Which repos have tracked large files?


The distribution workflow answers a different question:

- Which shared standard files should become the official source copy?
- And how do I safely distribute that standard file afterward?

Keep those two workflows separate.



## Recommended folder arrangement

A simple setup is:

- `~/R Working Directory/Master File Distribution Code`
    - stores your official standard files
    - stores `safe_master_file_distribution_helpers_v3.R`
    - stores this `.qmd` guide
- `~/R Working Directory/<project folders>`
    - contain evolving project-specific copies




## Step 0: Source the helper file

Use an explicit path.

```{r}
master_code_dir <- path.expand("~/R Working Directory/Master File Distribution Code")

source(file.path(
  master_code_dir,
  "SAFE_master_file_distribution_helpers_v3.R"
))
```



## Step 1: Inspect the default file set

```{r}
default_distribution_files("analysis")
```


Other built-in profiles:

```{r}
default_distribution_files("quarto_site")
default_distribution_files("minimal")
```




## Step 2: Find the most recent candidate copy of each shared file

### Why this step matters

Without this step, the workflow assumes the file currently sitting in `Master File Distribution Code` is the correct source copy.

That assumption can be wrong.

If you have been modifying shared files inside individual project folders, the newest and best copy may live in one of those project folders rather than in the master folder.

So the `find_most_recent_shared_files()` step gives you a better candidate source list before any audit or distribution happens.



```{r}
scan <- find_most_recent_shared_files()
```

The object named 'scan' contains:

- `scan$most_recent`
- `scan$all_matches`

The `most_recent` table shows the newest candidate file for each shared filename.

```{r}
scan$most_recent
```

The `all_matches` table shows every match that was found.

```{r}
scan$all_matches |> head(20)
```





## Step 3: Save the most-recent scan to Excel

```{r}
most_recent_file <- write_most_recent_shared_files_excel(
  scan,
  output_dir = "."
)

most_recent_file
```

The workbook includes:

- `most_recent`
- `all_matches`




## Important caution about "most recent"

The most recent file is the best **candidate** source copy.

It is **not automatic proof** that the file should become the official source.

Sometimes the newest file may be:
- a local experiment
- a partial edit
- a project-specific deviation
- a file changed only cosmetically

So you should review the `most_recent` sheet before promoting files into the master folder.




## Step 4: Promote selected files into the master folder

A dry run first:

```{r}
promotion_plan <- promote_files_to_master(
  selected_paths = scan$most_recent$path,
  dry_run = TRUE
)

promotion_plan
```


When satisfied, run the actual promotion:

```{r eval=FALSE}
promotion_result <- promote_files_to_master(
  selected_paths = scan$most_recent$path,
  update_current_as_of = TRUE,
  date_string = format(Sys.Date(), "%Y-%m-%d"),
  dry_run = FALSE
)
```



## About the `Current as of` line

In this workflow, the `Current as of` line is updated **during promotion to the master folder**, not as a separate earlier step.

That is intentional.

It means the date line now reflects:

> this file became the official master version on this date

That is a better interpretation than changing dates in many files before you have even decided which copy should become the official master.

The date-stamp update is applied only to supported file types, such as:

- `.gitattributes`
- `.gitignore`
- `.Rbuildignore`
- `.css`
- `.html`
- `.js`
- `.R`




## Step 5: Audit the distribution conflicts

```{r}
audit <- audit_distribution_conflicts()
audit |> head(20)
```




## Step 6: Summarize the audit

```{r}
summary <- summarize_distribution_audit(audit)
summary
```




## Step 7: Save the distribution audit to Excel

```{r}
audit_file <- write_distribution_audit_excel(
  audit,
  summary = summary,
  output_dir = "."
)

audit_file
```




## How to interpret the distribution statuses

The main status column is `compare_status`.

- `missing_source`: the source file is missing from the master folder
- `missing_destination`: the destination file does not exist
- `identical`: source and destination match
- `different_source_newer`: master source appears newer
- `different_destination_newer`: destination appears newer
- `different_same_or_unknown_time`: files differ but timestamps do not clearly settle it


The most important warning state is:

`different_destination_newer`

It may mean the project has a newer local version that you do not want to overwrite automatically.




## Step 8: Focus on the risky rows first

```{r}
audit |>
  dplyr::filter(compare_status %in% c(
    "different_destination_newer",
    "different_same_or_unknown_time"
  ))
```




## Step 9: Dry run the distribution plan

```{r}
plan <- distribute_project_files_safe(dry_run = TRUE)
```


Inspect the planned actions:

```{r}
plan |>
  dplyr::select(
    repo_name,
    file_name,
    compare_status,
    recommended_action,
    will_copy
  ) |>
  head(50)
```




## Step 10: Run the actual distribution

Only after reviewing the audit and dry run:

```{r eval=FALSE}
result <- distribute_project_files_safe(dry_run = FALSE)
```


Default protections are conservative:

- `overwrite_mode = "if_source_newer"`
- `protect_newer_destination = TRUE`
- `backup_before_overwrite = TRUE`




## Step 11: Final verification

This is the final check to confirm synchronization.

```{r}
audit_after <- audit_distribution_conflicts()

audit_after |>
  dplyr::count(compare_status, sort = TRUE)
```

If the workflow completed cleanly, this final table should show only:

- `identical`







## Most important principle

Do **not** think of this as:

> push the master files everywhere

Think of it as:

> identify the best candidate source file, promote it into the master folder, optionally stamp the master copy with the current date, audit the differences, then copy only when safe

That is the whole reason this workflow is safer than a blind overwrite workflow.



## Final recommendation

This workflow should replace the earlier distribution workflow.

It adds two important controls:

1. **find the most recent candidate source file first**
2. **update the `Current as of` line only when a file is promoted into the master folder**


